salad

### 2022-12-22 inst/salad.Rmd
rename columns in the interests of clarity

And second, slick:

```{r useslickmethod,cache=TRUE}
(H2 <- ordertable2supp(t(salad)))
```

>>>>

And second, a slick method.  We take the transpose of `salad` (things
are clearer if we name the rows):

```{r}
rownames(salad) <-
   paste("j",formatC(seq_len(nrow(salad)),width=2,format="d",flag="0"),sep="")
ts <- t(salad)
ts
```

Above, we see that object `ts` is an order table.  It is just like the
formula 1 result table `F1_table_2016`, except that venues are judges
and drivers are the salads [which are "competing" for the "who has the
most tart dressing" prize].  Converting this to a support function is
accomplished with `ordertable2supp()`:

```{r useslickmethod,cache=TRUE}
(H2 <- ordertable2supp(ts))
```
